\begin{remark}
	Let \( K \hookrightarrow L \) be a field extension, let \( a\in L \) be algebraic over \( K \).
	Let \( f \) be the minimal polynomial of \( a \) over \( K \). If \( b \) is some other root of \( f \) in some algebraic
	closure \( \overline{L} \) of \( L \), then \( f \) is also minimal polynomial of \( b \): We need
	to see that \( f(b) = 0 \), \( f \) monic, and irreducible.
	\begin{proof}
		By the fact that
		\[
			\begin{aligned}
				K(a) \cong   & \frac{K[x]}{(f)} \cong K(b)                  \\
				a \leftarrow & \; \; \; \overline{x}\; \; \;  \rightarrow b
			\end{aligned}
		\]
		then there exists an isomorphism of extension of \( K \):
		\[
			\begin{aligned}
				\sigma: K(a) & \xrightarrow{\sim} K(b) \\
				\sigma(a)    & = b
			\end{aligned}
		\]
	\end{proof}
\end{remark}

\begin{remark}
	The tensor product of \( K \)-algebra can be used to show the following:
	if \( K \hookrightarrow K_1 \) and \( K \hookrightarrow K_2 \) are two field extensions, then
	there exists a field \( K' \) with a commutative diagram of ring as follows:
	\[
		\begin{tikzcd}
			& K_1 \arrow[rd, hook] & \\
			K \arrow[ru, hook] \arrow[rd, hook] & & K' \\
			&K_2 \arrow[ru, hook] &
		\end{tikzcd}
	\]
	\begin{proof}
		We know that we have a commutative diagram of rings, given as follows:
		\[
			\begin{tikzcd}
				& K_1 \arrow[rd, hook] & \\
				K \arrow[ru, hook] \arrow[rd, hook] & & K_1\otimes_K K_2 \\
				&K_2 \arrow[ru, hook] &
			\end{tikzcd}
		\]
		with the morphism given by
		\[
			\begin{aligned}
				K_1 & \hookrightarrow K_1\otimes_K K_2 \\
				u   & \mapsto u\otimes 1               \\
				K_2 & \hookrightarrow K_1\otimes_K K_2 \\
				v   & \mapsto 1\otimes v
			\end{aligned}
		\]
		Notice that \( K_1 \otimes_K K_2 \ne 0 \), namely it is non-trivial ring, since we know the
		basis of it over \( K \) as \( K_1 \) and \( K_2 \) is free over \( K \). Thus there exists a
		maximal ideal \( M \) in \( K_1 \otimes_K K_2 \). Thus one can take
		\[
			K' \coloneqq \qo{K_1\otimes_K K_2}{M}
		\]
		which is a field intended, and the morhpism directly induced by the canonical morphism of
		quotient ring.
	\end{proof}
\end{remark}

\section{The Fundemental Theorem of Galois Theory}
We introduce the setup first, let \( K \hookrightarrow L \) be a finite Galois field extension,
namely it is normal and separable and algebraic. Now let
\[
	G \coloneqq G\bace{\qo{L}{K}} = \{\sigma : L \to L \in \Aut(L) \; | \; \sigma|_K = \Id_K\}
\]
and we have seen that
\[
	\abs{G} = [L:K] < \infty
\]
Out goal in this section is to \textbf{establish} a bijective correspondence between subextensions
\( K \hookrightarrow L' \hookrightarrow L \) and the subgroups of \( G \). We can make some simple
observations first:
\begin{itemize}
	\item If \( K \hookrightarrow L' \hookrightarrow L \) being a subextension, clearly
	      \[
		      G(\qo{L}{L'}) \leq G(\qo{L}{K})
	      \]
	      being subrgoup. \( \qo{L}{K} \) being a Galois extension \( \implies \qo{L}{L'} \) is \textbf{also} a Galois extension, thus
	      \[
		      \abs{G(\qo{L}{L'})} = [L:L'] < \infty
	      \]
	\item If \( H \leq G \) being a subgroup, define
	      \[
		      L^H \coloneqq  \{u\in L \; | \; \sigma(u) = u \; \forall \; \sigma \in H\}
	      \]
	      now since \( \sigma \) is a ring automorphism, we have \( 1 \in L^H \) and if \( u_1,u_2\in L^H \implies u_1 - u_2
	      \in L^H, u_1u_2 \in L^H \implies L^H \subseteq L\) being a subring. If \( u\in L^H
	      \smallsetminus \{0\} \implies u^{-1} \in L \implies u^{-1} \in L^H \) by the fact that \(
	      \sigma(u) = u \implies u^{-1} = (\sigma(u))^{-1} = \sigma(u^{-1}) \). Now it is easy to see that
	      \( K \subseteq L^H \) since \( \sigma \in G \implies \sigma|_K = \Id_K \implies \sigma(u) = u \;
	      \forall \; u \in K \implies \)
	      \[
		      K \hookrightarrow L^H \hookrightarrow L
	      \]
	      is a subextension.
\end{itemize}

\begin{theorem}[\textbf{Fundemental Theorem of Galois Theory}]
	Given in the finite extension setting:
	\begin{enumerate}
		\item These two maps describe above gives \textcolor{red}{mutual inverse order-reversing bijection} between
		      subextension of \( K \hookrightarrow L \) and subgroups of \( G \).
		\item The subgroup \( H \) of \( G \) is a normal subgroup of \( G \) iff \( K \hookrightarrow
		      L^H \) is a normal extension. In this case, we have an isormorphism:
		      \[
			      \qo{G}{H} \cong G\bace{\qo{L^H}{K}}
		      \]
	\end{enumerate}
\end{theorem}

\begin{note}
	This is probably the reason why people invent group. People can in this way describe the group
	structures completely with fields.
\end{note}

\begin{remark}
	Both maps we defined reverse inclusion, we illustrate what is \textcolor{red}{inverse
		order-reversing bijection} here:
	\begin{enumerate}
		\item If \( H_1 \subseteq H_2 \subseteq G(\qo{L}{K}) \implies L^{H_2} \subseteq L^{H_1} \).
		\item If \( K \hookrightarrow L_1 \hookrightarrow L_2 \hookrightarrow L \), then
		      \[
			      G\bace{\qo{L}{L_2}} \subseteq G\bace{\qo{L}{L_1}}
		      \]
	\end{enumerate}
\end{remark}

\begin{remark}
	For \textbf{1} in the \textbf{theorem}, we need to show:
	\begin{enumerate}
		\item If \( K \hookrightarrow L' \hookrightarrow L \implies L^{G(\qo{L}{L'})} = L' \).
		\item If \( H \leq G \) being subrgoup, then \( G(\qo{L}{L^H}) = H \).
	\end{enumerate}
\end{remark}

\begin{note}
	Notice that both ``\( \supseteq \)'' part is trivial follows from the definition.
\end{note}
We will then need to show in some sense both sides will have the same size/dimension:
\begin{itemize}
	\item For 1:
	      \[
		      [L : L^{G(\qo{L}{L'})}] = [L: L']
	      \]
	\item For 2:
	      \[
		      \abs{G(\qo{L}{L^H})} = \abs{H}
	      \]
\end{itemize}
And we then only need to show that for all \( H \leq G \), we have
\[
	[L:L^H] = \abs{H}
\]
We will need some preparations for it. Fix a field \( L \), if \( A \) be any set \( \Fun(A,L) = \{f: A \to L\} \)
being a \( L \)-vector space. By that
\[
	(\lambda f + \mu g) (a) = \lambda f(a) + \mu g(a) \quad \forall \; \lambda ,\mu \in L, f,g \in
	\Fun(A,L)
\]
\begin{theorem}[\textbf{Linear Independence of Characters}]
	If \( L \) is a field, \( H \) is a group and let
	\[
		\sigma _1,\ldots,\sigma _n : H \to L^\times
	\]
	be pairwise distinct group homomorphisms, then \( \sigma_1,\ldots, \sigma_n \in \Fun(H,L) \) are
	linearly independent over \( L \).
\end{theorem}

\begin{proof}
	Suppose there exists a relation \( a_1\sigma_1 + \cdots + a_n \sigma_n = 0 \), with not all \( a_i
	= 0\). WLOG, We can choose such relation with minimal \( n \), \( (\implies a_i \ne 0 \; \forall
	\; i) \). And we shall reason it through induction:
	\begin{itemize}
		\item If \( n = 1 \): \( a_1\sigma_1 = 0 \), leading to contradiction with \( a_1 \ne 0 \) and
		      \( \im(\sigma_1) \subseteq L \smallsetminus \{0\} = L^\times \).
		\item Suppose now \( n \geq 2 \): then by pairwise distinct, \( \sigma_1 \ne \sigma_2 \implies
		      \exists \; h \in H \), s.t. \( \sigma_1 (h) \ne \sigma_2 (h) \).
		      \[
			      \begin{aligned}
				      \text{Hypothesis} \implies \sum_{i=1}^n a_i \sigma_i (g) & = 0 \quad \forall \; g \in H \\
				      \implies \sum_{i=1}^n a_i \sigma_i (gh)                  & = 0 \quad \forall \; g \in H \\
				      \implies \sum_{i=1}^n a_i \sigma_i (g) \sigma_i (h)      & = 0
			      \end{aligned}
		      \]
		      Now multiply the first line with \( \sigma_1(h) \), we get
		      \[
			      \begin{aligned}
				      \implies \sum_{i=1}^n a_i \sigma_i (g) \sigma_1(h)                                                    & = 0 \quad \forall \; g \in H \\
				      \implies \sum_{i=2}^n a_i \underbrace{\sigma_i (h) - \sigma_1(h)}_{\ne 0 \text{ for } i = 2} \sigma_i & = 0
			      \end{aligned}
		      \]
		      Thus we get a non-trivial relation with smaller \( n \), which contradicts to the minimality
		      of \( n \).
	\end{itemize}
\end{proof}

\begin{corollary}
	If \( L \) is any field, then the element of \( \Aut(L) \) are linearly independent over \( L \).
\end{corollary}

\begin{proof}
	If \( \sigma_1,\ldots, \sigma_n \in \Aut(L) \) are distinct, then apply the theorem for
	\[
		\begin{aligned}
			\sigma_1 |_{L^\times} ,          &
			\ldots, \sigma_n |_{L^\times} \quad H = L^\times                                                     \\
			\implies \sigma _1|_{L^\times} , & \ldots,  \sigma_n |_{L^\times} \text{ are linearly independent}
			\\
			\implies \sigma_1,               & \ldots, \sigma _n \in \Fun(L,L) \text{ are linearly independent.}
		\end{aligned}
	\]
\end{proof}

\begin{proposition}
	\label{prop:lowerbound-automorphisms}
	Given a field \( L \), \( A \subseteq \Aut(L) \), let
	\[
		L' = \{u\in L \; | \; \sigma (u) = u \; \forall \; \sigma  \in A\}
	\]
	then
	\[
		[L: L'] \geq \# A
	\]
\end{proposition}

\begin{proof}
	May assume \( [L: L'] = n < \infty\) and there exists \( \sigma_1,\ldots,
	\sigma_{n+1} \in A \) are pairwise distinct. And we shall reason by contradiction. Suppose \(
	u_1,\ldots, u_n \in L \) is basis over \( L' \), consider the following linear system:
	\[
		\sum_{i=1}^{n+1} \underbrace{\sigma_i (u_j)}_{\in L} x_i = 0 \text{ for } 1 \leq j \leq n
	\]
	there are \( n \) equations with \( n+1 \) unknown variables, then there exists a solution \(
	(a_1,\ldots, a_{n+1}) \in L^{n+1} \), which is \( \ne (0,\ldots,0) \). Then
	\[
		\begin{aligned}
			\implies \sum_{i=1}^{n+1} a_i \sigma_i (u_j)      & = 0 \quad \forall \; j                      \\
			\implies \bace{\sum_{i=1}^{n+1} a_i \sigma_i} (u) & = 0 \quad \forall \; u \in L \text{ since }
			\sigma_i \text{ are } L'\text{-linear}
		\end{aligned}
	\]
	As we have \( \sigma_i (au) = \sigma_i (a)\sigma_i (u) = a\sigma_i(u) \) if \( a\in L' \).
	Thus we have \( \sigma_1,\ldots, \sigma_{n+1} \) are \textbf{\textcolor{blue}{linearly
			dependent}},
	contradicting to the corollary above.
\end{proof}
